%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------

  \cventry
    {Sr. Data Engineer} % Job title
    {Epidemic Sound} % Organization
    {Stockholm, Sweden} % Location
    {Jan. 2025 - present} % Date(s)
    {
    First data engineer on an early-stage team building a new product in a data-heavy domain.
    \vspace{5.0mm}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and built a data warehouse (DWH) and ELT data pipeline for large-scale social network data to support product features and mission-critical analytics.}
        \item {Design and implement self-serve data interfaces to large-scale, complex data for both internal and external customers.}
        \item {Prototyped quality metrics for evaluating the output of a foundational GenAI music model.}
        %\item {Own the DWH roadmap, continuously adapting to rapidly changing stakeholder requirements and market conditions.}
        %\item {Responsible for vendor negotiation and FinOps.}
      \end{cvitems}
    }

  \vspace{-1.0mm}
  \cventry
    {Data Science Team Lead} % Job title
    {} % Organization
    {} % Location
    {June 2024 - Jan. 2025} % Date(s)
    {
    Founding lead for a new team responsible for cultivating a data product culture within the data science domain.
    \vspace{5.0mm}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Articulated team vision after detailed discovery with data scientists, defined a roadmap, and got buy-in from leadership. }
        \item {Designed and implemented a technical toolkit for data product development that enabled traceability of ownership and automated error monitoring. }
        \item {Enhanced company's primary customer lifetime value model to support finer-grained cohorting while maintaining accuracy. }
        \item {Defined best practices around data product development, LLMs, and MLOps. Provided hands-on training to data scientists. }
        %\item {Prototyped two LLM-based analytics tools that were selected for development. }
      \end{cvitems}
    }

  \vspace{-1.0mm}
  \cventry
    {Sr. Analytics Engineer} % Job title
    {} % Organization
    {} % Location
    {Sept. 2023 - June 2024} % Date(s)
    {
    Epidemic's analytics engineering team owns our data warehouse and supports Epidemic's analysts
    and data scientists with tooling, data products, and expertise.
    \vspace{5.0mm}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and implemented a new pipeline code deployment process that significantly increased deployment frequency and reduced DWH downtime.}
        \item {Implemented DWH cost monitoring which was critical during renegotiation with GCP; stakeholder called it “a huge win”.}
        \item {Implemented DWH integration with new CRM tool; stakeholder said “never before in my career has an integration actually been delivered on time with no hiccups”.}
      \end{cvitems}
    }



%---------------------------------------------------------
  \cventry
    {Director of Engineering} % Job title
    {Bridgestone Mobility Solutions} % Organization
    {Stockholm, Sweden} % Location
    {Feb. 2021 - Aug. 2023} % Date(s)
    {
    My startup Mobikit (see below) was acquired and its product incorporated into Bridgestone's software portfolio as a data-driven fleet risk management product for insurance carriers called SafetyIQ. Post-acquisition, I integrated Mobikit with Bridgestone's engineering and sales orgs, and continued to lead product development for SafetyIQ.
    }

%---------------------------------------------------------
  \cventry
    {Co-founder/CTO} % Job title
    {Mobikit} % Organization
    {Columbus (OH), USA} % Location
    {Jan. 2019 - Feb. 2021} % Date(s)
    {
      Technical co-founder of a startup building a data analytics platform for large-scale vehicle telematics data. I oversaw data engineering, product development, and customer implementation.
      \vspace{5.0mm}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Architected and led development of distributed ETL data pipeline to ingest and enrich telematics data from heterogenous sources (millions of trips per month).}
        \item {Led design and development for data-driven features such as risk analytics, outlier detection, accident reconstruction, and more.}
        \item {Contributed code across the entire stack, from data pipeline to application backend to UI.}
        \item {Grew and managed globally distributed team of developers and data scientists, from interns to seniors (8 people at its heighest).}
        \item {Raised funding, guided company to product-market fit, and exited successfully.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Sr. Software Engineer} % Job title
    {Root Insurance} % Organization
    {Columbus (OH), USA} % Location
    {Sept. 2018 - Jan. 2019} % Date(s)
    {
      Worked at a growth-stage insuretech unicorn on multiple data-intensive projects.
      \vspace{5.0mm}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Prototyped a random forest model to enhance insurance rate accuracy.}
        \item {Implemented support for new rating methodologies and executed historical backtests for rating changes.}
        \item {Python SME for engineering and actuarial teams.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Lead Software Engineer} % Job title
    {Enlace Health} % Organization
    {Columbus (OH), USA} % Location
    {Sept. 2014 - Feb. 2018} % Date(s)
    {
      Enlace is a healthtech company building large-scale data analytics tools to support innovative models of healthcare delivery. I joined as an early employee working on the  analytics platform, and was then asked to lead a team building a new product.
      \vspace{5.0mm}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led a cross-functional team building a care management and revenue cycle management product for surgical centers.}
        \item {Owned product design and technical architecture, maintained product roadmap, implemented features.}
        \item {Designed and implemented a novel graph algorithm in Spark for processing healthcare claims data.}
        %\item {Introduced and trained engineering team on new technologies (Docker, Angular), development processes (TDD, code reviews), and agile methodology (user stories, estimation).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {InSample} % Organization
    {San Francisco (CA), USA} % Location
    {Mar. 2014 - Sept. 2014} % Date(s)
    {
      First employee at a healthcare analytics startup building a cloud-based tool for statistical de-biasing of clinical experiments. Together with the CTO, I interviewed prospective customers, and designed and built the product prototype.
      \vspace{3.0mm}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Google} % Organization
    {Mountain View (CA), USA} % Location
    {Feb. 2013 - Mar. 2014} % Date(s)
    {
      I was part of the conversion tracking team building tools that Google's customers use to understand the effectiveness of their ad spend. I implemented a novel conversion tracking visualization for the AdWords suite of analytics tools and developed enhancements to the Google Analytics Markov-chain-based attribution model.
      \vspace{3.0mm}
    }

%---------------------------------------------------------
  \cventry
    {Forward Deployed Engineer} % Job title
    {Palantir Technologies} % Organization
    {Palo Alto (CA), USA} % Location
    {Jan. 2011 - Jan. 2013} % Date(s)
    {
      I worked on Palantir's data integration and quantitative research platform for capital markets. I was a developer and product owner for the platform's visualization and reporting features, and was embedded with the platform's largest customer (Bridgewater Associates).
    }

%---------------------------------------------------------
\end{cventries}
